An Empirical Study of Invasion and Resistance for Iterated Prisoner's Dilemma Strategies

### 2017-05-10 main.tex
Adjust nb and rerun images.
Add tables for ZD strategies.

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Defector.pdf}
        \caption{Alternator and Defector}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

@@

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/WSLS_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WSLS.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_WSLS.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

@@

>>>>

\begin{figure}[!hbtp]
    \centering
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_Cooperator.pdf}
        \caption{Alternator and Cooperator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_Alternator.pdf}
        \caption{Defector and Alternator}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_TfT.pdf}
        \caption{Alternator and Tit For Tat}
    \end{subfigure}%

@@

    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/WStLSh_v_TfT.pdf}
        \caption{Win Stay Lose Shift and Tit For Tat}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Alternator_v_WStLSh.pdf}
        \caption{Alternator and Win Stay Lose Shift}
    \end{subfigure}%
    ~
    \begin{subfigure}[t]{.3\textwidth}
        \centering
        \includegraphics[width=.8\textwidth]{./img/Defector_v_WStLSh.pdf}
        \caption{Defector and Win Stay Lose Shift}
    \end{subfigure}%
    \caption{Comparison of theoretic and actual Moran Process fixation
             probabilities for \textbf{deterministic} strategies}
    \label{fig:comparison_deterministic}
\end{figure}

@@

% TODO Add discussion about ZD strategies

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{./tex/ZD_ranks_invade.tex}
    \caption{Ranks of Zero determinant strategies according to \(x_{1}\) for different
    population sizes}
    \label{tbl:ZD_ranks_v_invade}
\end{table}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{./tex/ZD_ranks_resist.tex}
    \caption{Ranks of Zero determinant strategies according to \(x_{N-1}\) for different
    population sizes}
    \label{tbl:ZD_ranks_v_size_resist}
\end{table}

\begin{table}[!hbtp]
    \centering
    \scriptsize
    \input{./tex/ZD_ranks_coexist.tex}
    \caption{Ranks of Zero determinant strategies according to \(x_{N/2}\) for different
    population sizes}
    \label{tbl:ZD_ranks_v_size_coexist}
\end{table}
